A Motion Capture and Imitation Learning-Based Approach to Robot Control

### 2022-06-20 tex-arxiv/article.tex
intro draft done

\paragraph{Motivating use case}

@@

In its simplest and most straightforward form -- sometimes referred to as \emph{behavioral cloning} -- it can be reduced to a classification or regression task. 
Given a set of states and actions or state transitions produced by an unknown expert function, a model (\emph{policy}) is trained to approximate this function. Even with very small parameter counts by modern standards, when combined with artificial neural networks this method has demonstrated some success as far back as the 1980s, provided a task with simple dynamics \citep{pomerleau1989alvinn}.

@@

asgasgasgagsagaga
asg

>>>>

To help guide the development process and serve as a means of evaluation, a sample use case was selected -- object throwing. While on the surface the task is almost entirely defined by elementary ballistics that can be programmed explicitly, it serves as a convenient benchmark for robot programming by way of demonstrations. The task was deemed sufficiently non-trivial when considered from the perspective of a Markov Decision Process or time-series model only given limited information about system state at any given time step, while also being suitable for intuitive evaluation by human observers due to its intuitively straightforward nature. Furthermore, the relationship between release position, velocity and target coordinates provides an obvious way to quantitatively evaluate model performance against training and validation data -- extrapolated throw accuracy.

\section{Preliminaries}
\label{sec:prelim}

@@

In its simplest and most straightforward form -- sometimes referred to as \emph{behavioral cloning} -- imitation learning can be reduced to a classification or regression task. Given a set of states and actions or state transitions produced by an unknown expert function, a model (\emph{policy}) is trained to approximate this function. Even with very small parameter counts by modern standards, when combined with artificial neural networks this method has demonstrated some success as far back as the 1980s, provided a task with simple dynamics \citep{pomerleau1989alvinn}.

@@
